Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
working on section of case study; i will submit the unfinished version, and update our submission later

\begin{figure}[tb]
	\centering
	\includegraphics[]{RemoveDentAndBump}
	\caption{Removing a dent by dilating and then remove a bump by eroding.
		(a) a polygon with a dent and a bump;
		(b) dilating the polygon in (a) with distance $d$ to remove the dent;
		(c) eroding the polygon in (b) with $2d$ to remove the bump;
		(d) dilating the polygon in (c) with $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemoveDentAndBump}
\end{figure}

At time $t$, we grow buildings with distance $\dtrm{G}$.
We dilate with distance $\dtrm{D}$ ($\dtrm{D}>0$),
erode with $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
and dilate back with $\dtrm{E}$.
A problem we may have is that 
a building may be split into several parts by erosion
(see \fig\ref{fig:ErosionBreak} for example).
The reason is that 
some parts of a building may be increased (by growing and dilating) 
with distance $\dtrm{G}+\dtrm{D}$, 
but can be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
If $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
and the building is not thick enough, 
a thin part may disappear.
In order to avoid this problem, we require that
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\end{equation}

@@

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
any dents and bumps narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$ in the map, 
which was used as a length threshold by, for example, 
\citet{Regnauld2001}.
Unfortunately, distance $\dtrm{G}$ can be arbitrarily small 
according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we set erosion distance
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
%Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
%$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
%t \cdot \frac{l}{2} M_\mathrm{g} >0$.
Still, we have to make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we need to make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} < \frac{2 d_\mathrm{G}}{l}.
\end{equation}

We wish to remove ``bays'' 
which have ``widths'' less than $2 r_\mathrm{h}$. 
Variable $r_\mathrm{h}= 2\sqrt{a_\mathrm{h}/\pi}$
is the radius of a hole which is just large enough to be presented on map.
Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ 
in the map.
Sometimes, our $\dtrm{D}$ is not large enough to do so 
because of the limitation from \eq\ref{eq:d_Dt}.
We define
\[
\dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
\]

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{BridgeMoreBuilding}
	\caption{Iteratively aggregating close buildings by adding bridges.
		(a) original buildings $p$, $q$, and~$r$.
		(b) growing the original buildings with distance $\dtrm{G}$.
		(c) buffering the grown buildings with distance $d_{\epsilon,t}/2$ 
		using round joins.
		(d) aggregating buildings $q$ and~$r$ by adding a bridge,
		as their buffer overlap each other in (c).
		(e) growing the buildings in (d) with distance $\dtrm{G}$.
		(f) buffering the grown buildings in (e) with distance 
		$d_{\epsilon,t}/2$ using round joins.
		(g) aggregating buildings $p$, $q$ and~$r$ by adding bridges.
		(h) growing the buildings in (g) with distance $\dtrm{G}$.
		(i) buffering the grown buildings in (h) with distance 
		$d_{\epsilon,t}/2$ using round joins.
	}
	\label{fig:BridgeMoreBuilding}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{Shrink_Uniting}
	\caption{Merging a polygon with the polygon at the immediately previous 
		step.
		(a) Merging the polygons of \fig\ref{fig:Shrink_Erosion}c and 
		\fig\ref{fig:Shrink_Erosion}g;
		(b) Merging the polygons of \fig\ref{fig:Shrink_Simplification}c and 
		\fig\ref{fig:Shrink_Simplification}h;
	}
	\label{fig:Shrink_Uniting}
\end{figure}

@@

@@

We set our goal scale at $1:50{,}000$ and $d_\mathrm{G}=25\,\mathrm{m}$
so that we can compare our result with the exiting data.
Also, this setting makes \eq\ref{eq:S_g} hold, 
where $M_\mathrm{g}=50{,}000$, $d_\mathrm{G}=25\,\mathrm{m}$, 
and $l=0.3\,\mathrm{mm}$.
In \eq\ref{eq:d_Dtmin}, the first part is always smaller than the second part 
according to our settings.
As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
according to \eq\ref{eq:d_Et} and $\alpha=1.5$.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics{GoalShape}
	\caption{Bridged original buildings 
		and goal shapes of the built-up areas (without removing small holes), 
		at scale $1:50{,}000$.
		There are $56$ built-up areas, which have $1{,}102$ edges in total.
	}
	\label{fig:GoalShape}
\end{figure*}

\begin{figure*}[tb]
	\centering
	\includegraphics{ExperimentalComparison}
	\caption{.
	}
	\label{fig:ExperimentalComparison}
\end{figure*}

The area on start map is $some number\,\text{mm}^2$.
Our area on map is $some number\,\text{mm}^2$.
According to \eq4 of paper \citet{Topfer1966}, 
the area on map should be $some number\,\text{mm}^2$

>>>>

\begin{figure}[tb]
	\centering
	\includegraphics[]{RemoveDentAndBump}
	\caption{Removing a dent by dilating and then remove a bump by eroding.
		(a) A polygon with a dent and a bump.
		(b) Dilating the polygon in (a) with distance $d$ to remove the dent.
		(c) Eroding the polygon in (b) with $2d$ to remove the bump.
		(d) Dilating the polygon in (c) with $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemoveDentAndBump}
\end{figure}

At time $t$, we grow buildings with distance $\dtrm{G}$.
We dilate with distance $\dtrm{D}$ ($\dtrm{D}>0$),
erode with $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
and dilate back with $\dtrm{E}$.
A problem we may have is that 
a building may be split into several parts by erosion
(see \fig\ref{fig:ErosionBreak} for example).
The reason is that 
some parts of a building may be increased (by growing and dilating) 
with distance $\dtrm{G}+\dtrm{D}$, 
but can be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
If $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
and the building is not thick enough, 
a thin part may disappear.
In order to avoid this problem, we require that
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\begin{equation}
\label{eq:d_DtBound}
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\end{equation}

@@

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
any dents and bumps narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$ in the map, 
which was used as a length threshold by, for example, 
\citet{Regnauld2001}.
Unfortunately, distance $\dtrm{G}$ can be arbitrarily small 
according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_DtBound}, where $\dtrm{D}>0$.
As a compromise, we set erosion distance
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
%Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
%$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
%t \cdot \frac{l}{2} M_\mathrm{g} >0$.
Still, we have to make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we need to make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} < \frac{2 d_\mathrm{G}}{l}.
\end{equation}

We wish to remove ``bays'' 
which have ``widths'' less than $2 r_\mathrm{h}$. 
Variable $r_\mathrm{h}= 2\sqrt{a_\mathrm{h}/\pi}$
is the radius of a hole which is just large enough to be presented on map.
Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ 
on map.
Sometimes, our $\dtrm{D}$ is not large enough to do so 
because of the limitation from \eq\ref{eq:d_DtBound}.
We define
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
\end{equation}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{BridgeMoreBuilding}
	\caption{Iteratively aggregating close buildings by adding bridges.
		(a) Original buildings $p$, $q$, and~$r$.
		(b) Growing the original buildings with distance $\dtrm{G}$.
		(c) Buffering the grown buildings with distance $d_{\epsilon,t}/2$ 
		using round joins.
		(d) Aggregating buildings $q$ and~$r$ by adding a bridge,
		as their buffer overlap each other in (c).
		(e) Growing the buildings in (d) with distance $\dtrm{G}$.
		(f) Buffering the grown buildings in (e) with distance 
		$d_{\epsilon,t}/2$ using round joins.
		(g) Aggregating buildings $p$, $q$ and~$r$ by adding bridges.
		(h) Growing the buildings in (g) with distance $\dtrm{G}$.
		(i) Buffering the grown buildings in (h) with distance 
		$d_{\epsilon,t}/2$ using round joins.
	}
	\label{fig:BridgeMoreBuilding}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{Shrink_Uniting}
	\caption{Merging a polygon with the polygon at the immediately previous 
		step.
		(a) Merging the polygons of \fig\ref{fig:Shrink_Erosion}c and 
		\fig\ref{fig:Shrink_Erosion}g.
		(b) Merging the polygons of \fig\ref{fig:Shrink_Simplification}c and 
		\fig\ref{fig:Shrink_Simplification}h.
	}
	\label{fig:Shrink_Uniting}
\end{figure}

@@

As mentioned in \sect\ref{sec:DilationErosion}, 
we remove holes that have area less than 
$a_\mathrm{h} = 8\,\mathrm{mm}^2$ on map.
The real area threshold for a hole at time $t$ is
\[
a_{\mathrm{h},t}=a_\mathrm{h}\cdot M_t^2.
\]

@@

We set our goal scale at $1:50{,}000$ and $d_\mathrm{G}=25\,\mathrm{m}$
so that we can compare our result with the exiting data.
Also, this setting makes \eq\ref{eq:S_g} hold, 
where $M_\mathrm{g}=50{,}000$, $d_\mathrm{G}=25\,\mathrm{m}$, 
and $l=0.3\,\mathrm{mm}$.
In \eq\ref{eq:d_Dt}, the first part is always smaller than the second part 
according to our settings.
As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
according to \eq\ref{eq:d_Et} and $\alpha=1.5$.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics{GoalShape}
	\caption{Bridged original buildings 
		and goal shapes of the built-up areas (without removing small holes), 
		at scale $1:50{,}000$.
		There are $56$ built-up areas, which have $1{,}102$ edges in total.
		We show a sequence of maps in \fig\ref{fig:ContinuousGeneralization} 
		for the region marked by the dashed circle.
	}
	\label{fig:GoalShape}
\end{figure*}

We produce a sequence of $10$ maps, which means $t \in \{0.1, 0.2, \dots, 1\}$.
This production cost $668.2\,\mathrm{s}$ in total.
We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
the marked region in \fig\ref{fig:GoalShape}.

\fig\ref{fig:ExperimentalComparison} shows a comparison of 
our result at time $t=1$
and the data from IGN at scale $1:50{,}000$.
No small buildings are removed in our result or the IGN data.
The boundaries of our built-up areas are more straight than that of IGN data, 
where we have $1{,}135$ edges while the data has $4{,}968$ edges.

\begin{figure*}[tb]
	\centering
	\includegraphics{ContinuousGeneralization}
	\caption{A sequence of maps at time $t \in \{0, 0.1, 0.2, \dots, 1\}$
		for the region marked in \fig\ref{fig:GoalShape}.
	}
	\label{fig:ContinuousGeneralization}
\end{figure*}

\begin{figure*}[tb]
	\centering
	\includegraphics{ExperimentalComparison}
	\caption{A comparison of our result and the existing data at scale 
	$1:50{,}000$.
		The brighter gray polygons represent the original buildings.
		The darker gray polygons are our result at time $t=1$.
		The gray polylines represent the data of the built-up areas at scale 
		$1:50{,}000$ from IGN, where some built-up areas are split because some 
		streets cross these areas.
	}
	\label{fig:ExperimentalComparison}
\end{figure*}

%The area on start map is $some number\,\text{mm}^2$.
%Our area on map is $some number\,\text{mm}^2$.
%According to \eq4 of paper \citet{Topfer1966}, 
%the area on map should be $some number\,\text{mm}^2$
